---
title: "Augmented Design (Analysis)"
author: "Oluwafemi Oyedele"
date: "`r format(Sys.Date())`"
output:
  html_document:
    toc_float: yes
    theme: darkly
    toc: yes
  word_document:
    toc: yes
fontfamily: serif
fontsize: 12pt
---

```{r setup, include = FALSE,echo=FALSE,message=FALSE,warning=FALSE}
library(tidyverse)
library(readxl)
library(augmentedRCBD)
library(factoextra)
library(correlation)
library(corrplot)
library(RColorBrewer)
library(corrr)
knitr::opts_chunk$set(echo = TRUE)
```

## Import the dataset into R
```{r}
pheno_dat <- read_excel(path = here::here('Data/Phenotypic data_Joy.xlsx'),sheet = 1) %>% janitor::clean_names() %>% 
  drop_na() %>% 
  group_by(collections) %>% 
  summarise_all(.funs = mean) %>% 
  column_to_rownames(var = 'collections')
```

## Farm Qualitative Traits (Diversity Analysis)


## Compute the Dissimilarity Matrix
```{r}
DIST <- dist(x = pheno_dat[,5:ncol(pheno_dat)],method = 'euclidean')
```

## Hierrachical Clusters
```{r}
Clust <- hclust(d = DIST,method = 'ward.D')
```

## Visualize the Cluster using base R
```{r}
plot(Clust)
```
## Visualize the Clusters using Factoextra
```{r}
fviz_dend(x = Clust,k = 3,k_colors = 'aaas',palette = 'aaas',rect = TRUE,rect_lty = 1,rect_fill = TRUE,main = '')+geom_hline(yintercept = 25,color='black')
```
## Save the Plot

```{r}
ggsave(filename = here::here('Plot/QualitativeTrait.png'),width = 10,height = 10,dpi = 300,bg = 'white')
```
## Market Qualitative
```{r}
market_qualitative <- read_excel(path = here::here('Data/Phenotypic data_Joy.xlsx'),sheet = 'Market_qualitative') %>% janitor::clean_names() %>% 
  drop_na() %>% 
  group_by(collections) %>% 
  summarise_all(.funs = mean) %>% 
  column_to_rownames(var = 'collections')
```


## Compute the Dissimilarity Matrix
```{r}
DIST <- dist(x = market_qualitative[,5:ncol(market_qualitative)],method = 'euclidean')
```

## Hierrachical Clusters
```{r}
Clust <- hclust(d = DIST,method = 'ward.D')
```

## Visualize the Cluster using base R
```{r}
plot(Clust)
```
## Visualize the Clusters using Factoextra
```{r}
fviz_dend(x = Clust,k = 3,k_colors = 'aaas',palette = 'aaas',rect = TRUE,rect_lty = 1,rect_fill = TRUE,main = '',repel = TRUE)+scale_y_continuous(expand = expansion(mult = c(0,0),add = c(0,1)))+
  theme(axis.text.y = element_text(family = 'serif',face = 'bold',size = 16,colour = 'black'),axis.title.y = element_text(family = 'serif',face = 'bold',colour = 'black',size = 16))
```
## Save the Plot

```{r}
ggsave(filename = here::here('Plot/Market_Qualitative.png'),width = 27,height = 12,dpi = 200,bg = 'white')
```




## Farm_quantitative

```{r}
farm_qualitative <- read_excel(path = here::here('Data/Phenotypic data_Joy.xlsx'),sheet = 'Farm_quantitative') %>% janitor::clean_names() %>% 
drop_na()
```

## Convert all the Characters to Factor
```{r}
farm_qualitative <- farm_qualitative %>% 
  mutate(across(.cols=c(1:4),.fns=factor))
```

## Fit the Model for days_to_emergence
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$days_to_emergence,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Fit the Model for petiole_length
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y =farm_qualitative$petiole_length,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```

## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Fit the Model for number_of_suckers_plant
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y =farm_qualitative$number_of_suckers_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```


## Fit the Model for number_of_stolons_plant
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y =farm_qualitative$number_of_stolons_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```

## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Fit the Model for leaf_length
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$leaf_length,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Fit the Model for leaf_width
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$leaf_width,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```

## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Fit the Model for leaf_length_width_ratio
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$leaf_length_width_ratio,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Fit the Model for leaf_area
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$leaf_area,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```

## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Fit the Model for plant_height
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$plant_height,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```


## Fit the Model for number_of_leaves_per_plant
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$number_of_leaves_per_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Fit the Model for plant_span
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$plant_span,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Fit the Model for flower_formation
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$flower_formation,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Fit the Model for number_of_corms_hill
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$number_of_corms_hill,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Fit the Model for number_of_cormels_hill
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$number_of_cormels_hill,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Fit the Model for total_weight
```{r}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$total_weight,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Correlation Analysis for Farm Qualitative
```{r}
farm_qualitative_corr <- farm_qualitative %>% select(5:19)

#corr <- correlation(farm_qualitative_corr,p_adjust = 'bonferroni',method = 'pearson',redundant = TRUE)

#corr

# summary(object = corr,redundant = TRUE) |> 
#   insight::print_html()

```

## Colour
```{r}
col<- colorRampPalette(c("red", "white", "blue"))(20)
```

```{r}
M<-cor(farm_qualitative_corr)

corrplot(corr = M,method = 'circle',type = 'upper',order = 'hclust',tl.col = 'black',col=col)

```

```{r}
x <- correlate(farm_qualitative_corr)

#autoplot(x)

autoplot(x, triangular = "lower")

#autoplot(x, triangular = "full")
```

## Save the Plot
```{r}
ggsave(filename = 'farm_quantitative_Corr.png',path = here::here('Plot'),width = 10,height = 10,dpi = 300,bg = 'white')
```

## Farm_quantitative_DM

```{r}
farm_quantitative_DM <- read_excel(path = here::here('Data/Phenotypic data_Joy.xlsx'),sheet = 'Farm_quantitative_DM') %>% janitor::clean_names() %>% drop_na() 
```

## Convert all the Characters to Factor
```{r}
farm_quantitative_tidy <- farm_quantitative_DM %>% 
  mutate(across(.cols=c(1:4),.fns=factor))
```

## Fit the Model for dry matter for Farm Quantitative DM
```{r}
model1 <- augmentedRCBD(farm_quantitative_tidy$block,treatment =farm_quantitative_tidy$collections,y=farm_quantitative_tidy$dry_matter,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```

## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```

## Market_quantitative

```{r}
market_quantitative <- read_excel(path = here::here('Data/Phenotypic data_Joy.xlsx'),sheet = 'Market_quantitative') %>% janitor::clean_names()
```

## Convert all the Characters to Factor
```{r}
market_quantitative_tidy <- market_quantitative |> 
mutate(across(.cols=c(1:4),.fns=factor))

market_quantitative_tidy <- market_quantitative_tidy |> 
mutate(across(.cols=c(6:7),.fns=as.numeric))
```

## Stop 2


### Stop Here the model size is too large

### This is where we are having issues

## Fit the Model for Plant Height
```{r}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$plant_height,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```


## Fit the Model for leaf_length
```{r}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$leaf_length,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for leaf_width
```{r}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$leaf_width,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
<!-- ## Fit the Model for leaf_length_width_ratio -->
<!-- ```{r} -->
<!-- market_quantitative_tidy <- market_quantitative %>%  -->
<!--   mutate(leaf_length_width_ratio=numeric(leaf_length_width_ratio)) -->


<!-- model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$leaf_length_width_ratio,checks = c('Check 1','Check 2'),method.comp = 'tukey') -->
<!-- ``` -->

## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for leaf_area
```{r}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$leaf_area,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for plant_span
```{r}

model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$plant_span,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for number_of_leaves_per_plant
```{r}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_leaves_per_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for number_of_suckers_plant
```{r}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_suckers_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for number_of_stolons_plant
```{r}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_stolons_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for flower_formation
```{r}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$flower_formation,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for number_of_corms_hill
```{r}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_corms_hill,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for number_of_cormels_hill
```{r}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_cormels_hill,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for total_weight
```{r}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$total_weight,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for dry_matter
```{r}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$dry_matter,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Market_quantitative_DM
```{r}
market_quantitative_DM <- read_excel(path = here::here('Data/Phenotypic data_Joy.xlsx'),sheet = 'Market_quantitative_DM') %>% janitor::clean_names() 
```

## Convert all the Characters to Factor
```{r}
market_quantitative_DM_tidy <- market_quantitative_DM %>% mutate(across(.cols=c(1:4),.fns=factor))
```

## Fit the Model for dry matter for market quantitative dry matter

```{r}
model1 <- augmentedRCBD(market_quantitative_DM_tidy$block,treatment=market_quantitative_DM_tidy$collections,y=market_quantitative_DM_tidy$dry_matter,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
