---
author: Oluwafemi OYEDELE
date: '`r format(Sys.Date())`'
title: NATACHA ANALYSIS
output:
  html_document:
    toc_float: true
    theme: darkly
    toc: true
fontfamily: serif
fontsize: 12pt
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Load the necessary library
```{r}
library(rio)
library(tidyverse)
library(factoextra)
library(readxl)
library(ggsci)
library(correlation)
```
# Import the dataset into R for Year 1

```{r}
dat1 <- read_excel(here::here('Data/TARO DATA NATACHA.xlsx'),skip = 2,sheet = 'year 1')
```

# Year One Analysis

# Prepare the dataset by adding rownames for all accessions
```{r}
dat11 <- dat1 |> select(5:15) |> group_by(Accessions) |> summarise_all(.funs = mean) |> column_to_rownames(var = 'Accessions')

```

# Calculate the dissimilarity matrix

```{r}
DT <- dist(x = dat11,method = 'euclidean')
```

# Computes the Clusters using base R

```{r}
Clust <- hclust(d = DT,method = 'ward.D')
```

# Visualize the cluster using base R
```{r}
plot(Clust)
```

# Visualize the Cluster using factoextra

```{r}
fviz_dend(x = Clust,k = 3,k_colors = 'aaas')+
  theme_void()
```
# Save the plot for year 1 cluster
```{r}
ggsave('year 1 Cluster.png',path = here::here('Plot'),width = 15,height = 8,dpi = 400,bg = 'white')
```

# Principal Component Analysis for Year 1

```{r}
dat <- dat1 |> select(-c(1:5)) |> drop_na() 
write.csv(x = dat,file = here::here('Data/Year One.csv'),row.names = FALSE)

PC <- prcomp(x = dat,center = TRUE,scale. = TRUE)

```
# Get the eigenvalues
```{r}
get_eigenvalue(X = PC)
```
# Summary of the PCA
```{r}
summary(PC)
```

# Screeplot
```{r}
fviz_screeplot(PC)
```

# Bi-Plot for Year One
```{r}
fviz_pca_biplot(X = PC)
```
# Save the Plot
```{r}
ggsave('PCA-Biplot for Year_One.png',path = here::here('Plot'),width = 15,height = 8,dpi = 400)
```

# Year One Correlation Analysis for both upper and lower diagonal
```{r}
dat <- dat1 |> select(-c(1:5))

res <- correlation(data = dat)

summary(object = res,redundant = TRUE) |> insight::print_html()
```

# Upper diagonal only
```{r}
dat <- dat1 |> select(-c(1:5))

res <- correlation(data = dat)

summary(object = res,redundant = FALSE) |> insight::print_html()
```


