---
title: "Data Analysis"
author: "Oluwafemi Oyedele"
format: html
editor: visual
---

# Load the necessary library

```{r}
#| echo: false
#| message: false
#| warning: false
library(readxl)
library(tidyverse)
library(augmentedRCBD)
```

# Import the dataset

```{r}
#| echo: false
#| message: false
#| warning: false

year_one <- read_excel(here::here('Data/TARO DATA NATACHA.xlsx'),sheet = 'year 1',skip = 2)

year_one <- year_one |>
  drop_na()

```

# Get the check for year one

```{r}
#| echo: false
#| message: false
#| warning: false

year_one_check <- c('P-K-I corm 2','P-K-I corm 6','P-K-I corm 5')

year_one <- year_one |> 
  mutate(across(.cols = c(1:5),.fns = factor))

```

# Year One Analysis

# Plant Height

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_one$Block,treatment = year_one$Accessions,y = year_one$PH,checks = year_one_check,method.comp = 'tukey',console = FALSE)

```

# NLP

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_one$Block,treatment = year_one$Accessions,y = year_one$NLP,checks = year_one_check,method.comp = 'tukey',console = FALSE)

```

# LL

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_one$Block,treatment = year_one$Accessions,y = year_one$LL,checks = year_one_check,method.comp = 'tukey',console = FALSE)

```

# LW

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_one$Block,treatment = year_one$Accessions,y = year_one$LW,checks = year_one_check,method.comp = 'tukey',console = FALSE)

```

# NOST

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_one$Block,treatment = year_one$Accessions,y = year_one$NOST,checks = year_one_check,method.comp = 'tukey',console = FALSE)

```

# NOSUP

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_one$Block,treatment = year_one$Accessions,y = year_one$NOSUP,checks = year_one_check,method.comp = 'tukey',console = FALSE)

```

# CL

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_one$Block,treatment = year_one$Accessions,y = year_one$CL,checks = year_one_check,method.comp = 'tukey',console = FALSE)

```

# CC

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_one$Block,treatment = year_one$Accessions,y = year_one$CC,checks = year_one_check,method.comp = 'tukey',console = FALSE)

```

# CW

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_one$Block,treatment = year_one$Accessions,y = year_one$CW,checks = year_one_check,method.comp = 'tukey',console = FALSE)

```

# WOCM

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_one$Block,treatment = year_one$Accessions,y = year_one$WOCM,checks = year_one_check,method.comp = 'tukey',console = FALSE)

```

# Import the dataset

```{r}
#| echo: false
#| message: false
#| warning: false

year_two <- read_excel(here::here('Data/TARO DATA NATACHA.xlsx'),sheet = 'year 2',skip = 2)

year_two <- year_two |>
  drop_na()

```

# Get the check for year one

```{r}
#| echo: false
#| message: false
#| warning: false

year_two_check <- c('P-K-I corm 5','P-K-I corm 6')

year_two <- year_two |> 
  mutate(across(.cols = c(1:5),.fns = factor))

```

# Year Two Analysis

# Plant Height

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_two$Block,treatment = year_two$Accessions,y = year_two$PH,checks = year_two_check,method.comp = 'tukey',console = FALSE)

```

# NLP

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_two$Block,treatment = year_two$Accessions,y = year_two$NLP,checks = year_two_check,method.comp = 'tukey',console = FALSE)

```

# LL

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_two$Block,treatment = year_two$Accessions,y = year_two$LL,checks = year_two_check,method.comp = 'tukey',console = FALSE)

```

# LW

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_two$Block,treatment = year_two$Accessions,y = year_two$LW,checks = year_two_check,method.comp = 'tukey',console = FALSE)

```

# NOST

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_two$Block,treatment = year_two$Accessions,y = year_two$NOST,checks = year_one_check,method.comp = 'tukey',console = FALSE)

```

# NOSUP

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_two$Block,treatment = year_two$Accessions,y = year_two$NOSUP,checks = year_two_check,method.comp = 'tukey',console = FALSE)

```

# CL

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_two$Block,treatment = year_two$Accessions,y = year_two$CL,checks = year_two_check,method.comp = 'tukey',console = FALSE)

```

# CC

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_two$Block,treatment = year_two$Accessions,y = year_two$CC,checks = year_two_check,method.comp = 'tukey',console = FALSE)

```

# CW

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_two$Block,treatment = year_two$Accessions,y = year_two$CW,checks = year_two_check,method.comp = 'tukey',console = FALSE)

```

# WOCM

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = year_two$Block,treatment = year_two$Accessions,y = year_two$WOCM,checks = year_two_check,method.comp = 'tukey',console = FALSE)

```

# Combined Analysis

# Import the dataset

```{r}
#| echo: false
#| message: false
#| warning: false

combined <- read_excel(here::here('Data/TARO DATA NATACHA.xlsx'),sheet = 'combined data year1 year2',skip = 2)

combined <- combined |>
  drop_na()

```

# Get the check for year one

```{r}
#| echo: false
#| message: false
#| warning: false

combined_check <- c('P-K-I corm 2','P-K-I corm 6','P-K-I corm 5')

combined <- combined |> 
  mutate(across(.cols = c(1:5),.fns = factor))

```

# Combined Analysis

# Plant Height

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = combined$Block,treatment = combined$Accessions,y = combined$PH,checks = combined_check,method.comp = 'tukey',console = FALSE)

```

# NLP

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = combined$Block,treatment = combined$Accessions,y = combined$NLP,checks = combined_check,method.comp = 'tukey',console = FALSE)

```

# LL

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = combined$Block,treatment = combined$Accessions,y = combined$LL,checks = combined_check,method.comp = 'tukey',console = FALSE)

```

# LW

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = combined$Block,treatment = combined$Accessions,y = combined$LW,checks = combined_check,method.comp = 'tukey',console = FALSE)

```

# NOST

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = combined$Block,treatment = combined$Accessions,y = combined$NOST,checks = combined_check,method.comp = 'tukey',console = FALSE)

```

# NOSUP

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = combined$Block,treatment = combined$Accessions,y = combined$NOSUP,checks = combined_check,method.comp = 'tukey',console = FALSE)

```

# CL

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = combined$Block,treatment = combined$Accessions,y = combined$CL,checks = combined_check,method.comp = 'tukey',console = FALSE)

```

# CC

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = combined$Block,treatment = combined$Accessions,y = combined$CC,checks = combined_check,method.comp = 'tukey',console = FALSE)

```

# CW

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = combined$Block,treatment = combined$Accessions,y = combined$CW,checks = combined_check,method.comp = 'tukey',console = FALSE)

```

# WOCM

```{r}
#| echo: false
#| message: false
#| warning: false

augmentedRCBD(block = combined$Block,treatment = combined$Accessions,y = combined$WOCM,checks = combined_check,method.comp = 'tukey',console = FALSE)

```
