---
author: Oluwafemi OYEDELE
date: '`r format(Sys.Date())`'
title: T Test Analysis
output:
  html_document:
    toc_float: true
    theme: darkly
    toc: true
fontfamily: serif
fontsize: 12pt
---

```{r setup, include = FALSE,echo=FALSE,warning=FALSE,message=FALSE}
library(readxl) # Read Excel Files
library(tidyverse) # Easily Install and Load the 'Tidyverse'
library(report) # Automated Reporting of Results and Statistical Models
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=FALSE,warning=FALSE,message=FALSE}
data <- read_excel('Data/T-TEST ANALYSIS.xlsx')
```

# Analysis for Co
```{r,echo=FALSE,warning=FALSE,message=FALSE}
t.test(data$Co~data$TREATMENT)
```
# Interpretation of the result for Co against Treatment using the report function in R  
```{r,echo=FALSE,warning=FALSE,message=FALSE}
t.test(data$Co~data$TREATMENT) %>% report()
```

# Analysis for Cr
```{r,echo=FALSE,warning=FALSE,message=FALSE}
t.test(data$Cr~data$TREATMENT)
```

# Interpretation of the result for Cr against Treatment using the report function in R  
```{r,echo=FALSE,warning=FALSE,message=FALSE}
t.test(data$Cr~data$TREATMENT) %>% report()
```

# Analysis for Cd
```{r,echo=FALSE,warning=FALSE,message=FALSE}
t.test(data$Cd~data$TREATMENT)
```
# Interpretation of the result for Cd against Treatment using the report function in R
```{r,echo=FALSE,warning=FALSE,message=FALSE}
t.test(data$Cd~data$TREATMENT) %>% report()
```

# Analysis for Pb
```{r,echo=FALSE,warning=FALSE,message=FALSE}
t.test(data$Pb~data$TREATMENT)
```

# Interpretation for Pb
```{r,echo=FALSE,warning=FALSE,message=FALSE}
t.test(data$Pb~data$TREATMENT) %>% report()
```

# Analysis for Ni
```{r,echo=FALSE,warning=FALSE,message=FALSE}
t.test(data$Ni~data$TREATMENT)
```
# Interpretation for Ni
```{r,echo=FALSE,warning=FALSE,message=FALSE}
t.test(data$Ni~data$TREATMENT) %>% report()
```

