---
author: Oluwafemi OYEDELE
date: '`r format(Sys.Date())`'
title: Analysis of Variance
output:
  html_document:
    toc_float: true
    theme: darkly
    toc: true
fontfamily: serif
fontsize: 12pt
---

# Load the necessary R package
```{r setup, include = FALSE}
library(tidyverse)
library(agricolae)
library(MetBrewer)
library(report)
library(readxl)
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)
```

# Set the path to import the sheet
```{r}
path <- here::here('Data/THOLAR GROWTH PARAMETER MAY & AUG.xlsx')

```

# Import the excel sheet
```{r}
walk(.x = excel_sheets(path = path),.f = ~assign(tolower(.x),read_excel(path = path,sheet = .x),envir = .GlobalEnv))
```

# Leaf Area
```{r}
Leaf_Area <- `leaf area` |> 
  pivot_longer(cols = 6:ncol(`leaf area`),names_to = 'Week',names_prefix = 'LAWK',values_to = 'LA') |> 
  relocate(Week,REP,.after = MONTH) |> 
  mutate(across(.cols = c(1:6),.fns = factor)) #Assign the result to a new variable
```

# Fit the Model for Leaf Area
```{r}
mod <- lm(LA~REP+LOCATION*MONTH*Week*VARIETY*TRT,data=Leaf_Area)

anova(mod)
report(anova(mod))
cv.model(mod)

HSD.test(y = mod,trt = 'LOCATION',console = TRUE)
HSD.test(y = mod,trt = 'MONTH',console = TRUE)
HSD.test(y = mod,trt = 'Week',console = TRUE)
HSD.test(y = mod,trt = 'Variety',console = TRUE)
HSD.test(y = mod,trt = 'TRT',console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','MONTH'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','Week'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','Week'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('Week','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('Week','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','MONTH','Week'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','Week','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','VARIETY','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','Week','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','VARIETY','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('Week','VARIETY','TRT'),console = TRUE)

HSD.test(y = mod,trt = c('LOCATION','MONTH','Week','VARIETY','TRT'),console = TRUE)
```

# Number of Leaf

```{r}
Number_of_Leaf <- `number of leaf` |> 
  pivot_longer(cols = 6:ncol(`number of leaf`),names_to = 'Week',names_prefix = 'NLWK',values_to = 'NL') |> 
  relocate(Week,REP,.after = MONTH) |> 
  mutate(across(.cols = c(1:6),.fns = factor)) #Assign the result to a new variable
```

# Fit the Model for Number of Leaf
```{r}
mod <- lm(NL~REP+LOCATION*MONTH*Week*VARIETY*TRT,data=Number_of_Leaf)

anova(mod)
report(anova(mod))
cv.model(mod)

HSD.test(y = mod,trt = 'LOCATION',console = TRUE)
HSD.test(y = mod,trt = 'MONTH',console = TRUE)
HSD.test(y = mod,trt = 'Week',console = TRUE)
HSD.test(y = mod,trt = 'Variety',console = TRUE)
HSD.test(y = mod,trt = 'TRT',console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','MONTH'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','Week'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','Week'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('Week','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('Week','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','MONTH','Week'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','Week','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','VARIETY','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','Week','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','VARIETY','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('Week','VARIETY','TRT'),console = TRUE)

HSD.test(y = mod,trt = c('LOCATION','MONTH','Week','VARIETY','TRT'),console = TRUE)
```

# Stem Diameter


```{r}
Stem_Diameter <- `stem diameter` |> 
  pivot_longer(cols = 6:ncol(`stem diameter`),names_to = 'Week',names_prefix = 'SD',values_to = 'SD') |> 
  relocate(Week,REP,.after = MONTH) |> 
  mutate(across(.cols = c(1:6),.fns = factor)) #Assign the result to a new variable
```

# Fit the Model for Stem Diameter
```{r}
mod <- lm(SD~REP+LOCATION*MONTH*Week*VARIETY*TRT,data=Stem_Diameter)

anova(mod)
report(anova(mod))
cv.model(mod)

HSD.test(y = mod,trt = 'LOCATION',console = TRUE)
HSD.test(y = mod,trt = 'MONTH',console = TRUE)
HSD.test(y = mod,trt = 'Week',console = TRUE)
HSD.test(y = mod,trt = 'Variety',console = TRUE)
HSD.test(y = mod,trt = 'TRT',console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','MONTH'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','Week'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','Week'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('Week','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('Week','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','MONTH','Week'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','Week','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','VARIETY','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','Week','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','VARIETY','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('Week','VARIETY','TRT'),console = TRUE)

HSD.test(y = mod,trt = c('LOCATION','MONTH','Week','VARIETY','TRT'),console = TRUE)
```


# Stem Height
```{r}
Stem_Height <- `stem height` |> 
  pivot_longer(cols = 6:ncol(`stem height`),names_to = 'Week',names_prefix = 'SH',values_to = 'SH') |> 
  relocate(Week,REP,.after = MONTH) |> 
  mutate(across(.cols = c(1:6),.fns = factor)) #Assign the result to a new variable
```

# Fit the Model for Stem Height
```{r}
mod <- lm(SH~REP+LOCATION*MONTH*Week*VARIETY*TRT,data=Stem_Height)

anova(mod)
report(anova(mod))
cv.model(mod)

HSD.test(y = mod,trt = 'LOCATION',console = TRUE)
HSD.test(y = mod,trt = 'MONTH',console = TRUE)
HSD.test(y = mod,trt = 'Week',console = TRUE)
HSD.test(y = mod,trt = 'Variety',console = TRUE)
HSD.test(y = mod,trt = 'TRT',console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','MONTH'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','Week'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','Week'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('Week','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('Week','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','MONTH','Week'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','Week','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('LOCATION','VARIETY','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','Week','VARIETY'),console = TRUE)
HSD.test(y = mod,trt = c('MONTH','VARIETY','TRT'),console = TRUE)
HSD.test(y = mod,trt = c('Week','VARIETY','TRT'),console = TRUE)

HSD.test(y = mod,trt = c('LOCATION','MONTH','Week','VARIETY','TRT'),console = TRUE)
```

# Interraction Plot for Leaf Area

# What are the names of the Varieties ?
```{r,echo = FALSE,message = FALSE,warning = FALSE}
plot <- `leaf area` |> pivot_longer(cols = -c(1:5),names_prefix = 'LAWK') |> mutate(MONTH=factor(MONTH,levels = c('MAY','AUGUST'))) |> 
  mutate(name=factor(name,levels = c(1:10))) |>
  mutate(VARIETY=factor(VARIETY)) |> 
  group_by(name) |> 
  drop_na() |> 
  ggplot(aes(x = TRT,y = value,fill=fct_reorder2(.f = VARIETY,.x = TRT,.y = value,.desc = FALSE)))+
  stat_summary(geom = 'errorbar',position = 'dodge',fun.data = mean_se)+
  stat_summary(geom = 'col',position = position_dodge(.9),fun = 'mean')+
  scale_fill_met_d(name = 'Hokusai1')+
  facet_grid(LOCATION~MONTH)+
  scale_y_continuous(expand = expansion(mult = c(0,.1)))+
  theme_test()+
  labs(x='Treatment',y='Leaf Area',fill='Variety')+
  theme(axis.text.y = element_text(family = 'serif',colour = 'black',face = 'bold',size = 15),
        panel.background = element_rect(colour = 'black'),panel.grid = element_blank(),axis.text.x = element_text(family = 'serif',colour = 'black',face = 'bold',size = 15,hjust = 1,angle = 45),axis.title = element_text(family = 'serif',colour = 'black',face = 'bold',size = 15),legend.title = element_text(family = 'serif',colour = 'black',face = 'bold',size = 15),legend.text = element_text(family = 'serif',colour = 'black',face = 'bold',size = 15),strip.text = element_text(family = 'serif',colour = 'black',face = 'bold',size = 15))
```

# Save the plot for Leaf Area

```{r}
ggsave(filename = 'THOLAR_Growth_Parameter/Leaf_Area/Location_Month_Varieties_TRT/Leaf_Area.png',plot = plot,device = 'png',path = here::here('Plot'),width = 12,height = 10,dpi = 400,bg = 'white')
```


# Interraction Plot for Leaf Number


# What is the value of Varieties ?


```{r,echo = FALSE,message = FALSE,warning = FALSE}
plot <- `number of leaf` |> pivot_longer(cols = -c(1:5),names_prefix = 'NLWK') |> mutate(MONTH=factor(MONTH,levels = c('MAY','AUGUST'))) |> 
  mutate(name=factor(name,levels = c(1:10))) |> 
  mutate(VARIETY=factor(VARIETY)) |>  # What is the value of Varieties ?
  group_by(name) |> 
  ggplot(aes(x = name,y = value,col=MONTH,group=MONTH))+
  stat_summary(geom = 'errorbar',position = 'dodge',fun.data = 'mean_se',size=1)+
  stat_summary(geom = 'line',position = position_dodge(.9),fun = 'mean')+
  stat_summary(geom = 'point',position = position_dodge(.9),fun = 'mean',size=1)+
  scale_color_met_d(name = 'Lakota')+
  labs(x='Time (Weeks)',y='Number of Leaf',col=NULL)+
  facet_grid(~LOCATION)+
  theme_test()+
  theme(text=element_text(family = 'serif',size = 14,colour = 'black'),
        strip.background = element_rect(fill = 'white',colour = 'black'),legend.position ='top',axis.text = element_text(family = 'serif',colour = 'black',size = 14),axis.ticks = element_line(colour = 'black',size = 1,linetype = 'solid'))
```

# Save the plot for Number of Leaf

```{r}
ggsave(filename = 'THOLAR_Growth_Parameter/Leaf_Number/LOCATION_MONTH_Week/Number_of_Leaf.png',plot = plot,device = 'png',path = here::here('Plot'),width = 10,height = 8,dpi = 400,bg = 'white')
```


# Interraction Plot for Leaf Number  (Location_Week_Variety)
```{r,echo = FALSE,message = FALSE,warning = FALSE}
plot <- `number of leaf` |> pivot_longer(cols = -c(1:5),names_prefix = 'NLWK') |> mutate(MONTH=factor(MONTH,levels = c('MAY','AUGUST'))) |> 
  mutate(name=factor(name,levels = c(1:10))) |> 
  mutate(VARIETY=factor(VARIETY)) |>  # What is the value of Varieties ?
  group_by(name) |> 
  ggplot(aes(x = name,y = value,col=MONTH,group=MONTH))+
  stat_summary(geom = 'errorbar',position = 'dodge',fun.data = 'mean_se',size=1)+
  stat_summary(geom = 'line',position = position_dodge(.9),fun = 'mean')+
  stat_summary(geom = 'point',position = position_dodge(.9),fun = 'mean',size=1)+
  scale_color_met_d(name = 'Lakota')+
  labs(x='Time (Weeks)',y='Number of Leaf',col=NULL)+
  facet_grid(~VARIETY)+
  theme_test()+
  theme(text=element_text(family = 'serif',size = 14,colour = 'black'),
        strip.background = element_rect(fill = 'white',colour = 'black'),legend.position ='top',axis.text = element_text(family = 'serif',colour = 'black',size = 14),axis.ticks = element_line(colour = 'black',size = 1,linetype = 'solid'))
```

# Save the plot for Leaf Number

```{r}
ggsave(filename = 'THOLAR_Growth_Parameter/Leaf_Number/Month_Week_VARIETY/Leaf_Number.png',plot = plot,device = 'png',path = here::here('Plot'),width = 10,height = 8,dpi = 400,bg = 'white')
```




# Interraction Plot of Location_Month_Week

# What are the names of the varieties ?


# Correct the colours and the procced to the next Visualization
```{r,echo = FALSE,message = FALSE,warning = FALSE}
plot <- `number of leaf` |> pivot_longer(cols = -c(1:5),names_prefix = 'NLWK') |> mutate(MONTH=factor(MONTH,levels = c('MAY','AUGUST'))) |> 
  mutate(name=factor(name,levels = c(1:10))) |> 
  mutate(VARIETY=factor(VARIETY)) |>  # What is the value of Varieties ?
  group_by(name) |> 
  ggplot(aes(x = name,y = value,col=TRT,group=TRT))+
  stat_summary(geom = 'errorbar',position = 'dodge',fun.data = 'mean_se',size=1)+
  stat_summary(geom = 'line',position = position_dodge(.9),fun = 'mean')+
  stat_summary(geom = 'point',position = position_dodge(.9),fun = 'mean',size=1)+
  #scale_color_brewer(palette = 'Set1')+
  scale_color_manual(values = c("black","green","blue","gray75","red","lightblue","purple"))+
  labs(x='Time (Week)',y='Number of Leaf',col=NULL)+
  facet_grid(~MONTH)+
  theme_test()+
  theme(text=element_text(family = 'serif',size = 14,colour = 'black'),
        strip.background = element_rect(fill = 'white',colour = 'black'),legend.position ='top',axis.text = element_text(family = 'serif',colour = 'black',size = 14),axis.ticks = element_line(colour = 'black',size = 1,linetype = 'solid'))
```

# Save the plot for Leaf Number

```{r}
ggsave(filename = 'THOLAR_Growth_Parameter/Leaf_Number/Month_Week_TRT/Leaf_Number.png',plot = plot,device = 'png',path = here::here('Plot'),width = 10,height = 8,dpi = 400,bg = 'white')
```


# Interraction Plot for Stem Diameter  (Month_Variety)
# What are the names of the varieties ?

```{r,echo = FALSE,message = FALSE,warning = FALSE}
plot <- `stem diameter` |>select(1:15) |> pivot_longer(cols = -c(1:5),names_prefix = 'SD') |> mutate(MONTH=factor(MONTH,levels = c('MAY','AUGUST'))) |> 
  mutate(name=factor(name,levels = c(1:10))) |> 
  mutate(VARIETY=factor(VARIETY,levels =c(1,2,3,4))) |> 
  group_by(name) |> 
  ggplot(aes(x = name,y = value,col=LOCATION,group=LOCATION))+
  stat_summary(geom = 'line',fun = 'mean',size=1,position = position_dodge(.9))+
  stat_summary(geom = 'point',fun = 'mean',size=2,position = position_dodge(.9))+
  stat_summary(geom = 'errorbar',position = position_dodge(.5),fun.data = mean_se,size=1)+
  scale_color_met_d(name = 'Hokusai1')+
  coord_cartesian(ylim = c(0,15))+
  facet_grid(~MONTH)+
  labs(colour='Location',x=str_to_title('Time (Weeks)'),y= str_to_title('Stem Diameter'))+
  theme_test()+
  theme(text=element_text(family = 'serif',size = 14,colour = 'black'),
        strip.background = element_rect(fill = 'white',colour = 'black'),legend.position ='right',axis.text = element_text(family = 'serif',colour = 'black',size = 14),axis.ticks = element_line(colour = 'black',size = 1,linetype = 'solid'))
```

# Save the plot for Stem Diameter

```{r}
ggsave(filename = 'THOLAR_Growth_Parameter/Stem_Diameter/Location_Month_Week/Stem_Diameter.png',plot = plot,device = 'png',path = here::here('Plot'),width = 10,height = 8,dpi = 400,bg = 'white')
```


# Interraction Plot (Location_Month_Variety)

# What are the names of the varieties ?

```{r,echo = FALSE,message = FALSE,warning = FALSE}
plot <- `stem diameter` |>select(1:15) |> pivot_longer(cols = -c(1:5),names_prefix = 'SD') |> mutate(MONTH=factor(MONTH,levels = c('MAY','AUGUST'))) |> 
  mutate(name=factor(name,levels = c(1:11))) |> 
  mutate(VARIETY=factor(VARIETY,levels =c(1,2,3,4))) |> 
  group_by(name) |> 
  ggplot(aes(x = VARIETY,y = value,fill=MONTH))+
  stat_summary(geom = 'errorbar',fun.data  = 'mean_se',position = 'dodge',size=0.7)+
  stat_summary(geom = 'col',fun = 'mean',position =position_dodge(.9))+
  scale_fill_met_d(name = 'Lakota')+
  coord_cartesian(ylim = c(0,15),expand = FALSE,clip = 'off')+
  facet_wrap(~LOCATION)+
  labs(fill='',x='Variety',y= str_to_title('Stem Diameter'))+
  theme_test()+
  theme(text=element_text(family = 'serif',size = 14,colour = 'black'),
        strip.background = element_rect(fill = 'white',colour = 'black'),legend.position ='top',axis.text = element_text(family = 'serif',colour = 'black',size = 14),axis.ticks = element_line(colour = 'black',size = 1,linetype = 'solid'))
```

# Save the plot for Stem Diameter

```{r}
ggsave(filename = 'THOLAR_Growth_Parameter/Stem_Diameter/Location_Month_Variety/Stem_Diameter.png',plot = plot,device = 'png',path = here::here('Plot'),width = 10,height = 8,dpi = 400,bg = 'white')
```



# Interraction Plot for (Location _Month_Week)

```{r,echo = FALSE,message = FALSE,warning = FALSE}
plot <- `stem height` |>select(1:15) |> pivot_longer(cols = -c(1:5),names_prefix = 'SH') |> mutate(MONTH=factor(MONTH,levels = c('MAY','AUGUST'))) |> 
  mutate(name=factor(name,levels = c(1:10))) |> 
  mutate(VARIETY=factor(VARIETY,levels =c(1,2,3,4))) |> 
  group_by(name) |> 
  ggplot(aes(x = name,y = value,col=LOCATION,group=LOCATION))+
  stat_summary(geom = 'line',fun = 'mean',size=1,position = position_dodge(.9))+
  stat_summary(geom = 'point',fun = 'mean',size=2,position = position_dodge(.9))+
  stat_summary(geom = 'errorbar',position = position_dodge(.5),fun.data = mean_se,size=1)+
  scale_color_met_d(name = 'Hokusai1')+
  coord_cartesian(ylim = c(0,15))+
  facet_grid(~MONTH)+
  labs(colour='Location',x=str_to_title('Time (Weeks)'),y= str_to_title('Stem Height'))+
  theme_test()+
  theme(text=element_text(family = 'serif',size = 14,colour = 'black'),
        strip.background = element_rect(fill = 'white',colour = 'black'),legend.position ='right',axis.text = element_text(family = 'serif',colour = 'black',size = 14),axis.ticks = element_line(colour = 'black',size = 1,linetype = 'solid'))
```



# Save the plot for Stem Height

```{r}
ggsave(filename = 'THOLAR_Growth_Parameter/Stem_Height/Location_Month_Week/Stem_Height1.png',plot = plot,device = 'png',path = here::here('Plot'),width = 10,height = 8,dpi = 400,bg = 'white')
```


# Stem Height

# Location_Month_Variety

```{r,echo = FALSE,message = FALSE,warning = FALSE}
plot <- `stem diameter` |>select(1:15) |> pivot_longer(cols = -c(1:5),names_prefix = 'SH') |> mutate(MONTH=factor(MONTH,levels = c('MAY','AUGUST'))) |> 
  mutate(name=factor(name,levels = c(1:11))) |> 
  mutate(VARIETY=factor(VARIETY,levels =c(1,2,3,4))) |> 
  group_by(name) |> 
  ggplot(aes(x = VARIETY,y = value,fill=LOCATION))+
  stat_summary(geom = 'errorbar',fun.data  = 'mean_se',position = 'dodge',size=0.7)+
  stat_summary(geom = 'col',fun = 'mean',position =position_dodge(.9))+
  scale_fill_met_d(name = 'Lakota')+
  #coord_cartesian(ylim = c(0,15),expand = FALSE,clip = 'off')+
  scale_y_continuous(expand = expansion(mult = c(0,.1)))+
  facet_grid(~MONTH)+
  labs(fill='',x='Variety',y= str_to_title('Stem Height'))+
  theme_test()+
  theme(text=element_text(family = 'serif',size = 14,colour = 'black'),
        strip.background = element_rect(fill = 'white',colour = 'black'),legend.position ='top',axis.text = element_text(family = 'serif',colour = 'black',size = 14),axis.ticks = element_line(colour = 'black',size = 1,linetype = 'solid'))
```



```{r}
ggsave(filename = 'THOLAR_Growth_Parameter/Stem_Height/Location_Month_Variety/Stem_Height2.png',plot = plot,device = 'png',path = here::here('Plot'),width = 10,height = 8,dpi = 400,bg = 'white')
```
